---
title: "Final assessment"
Author: Kun Cheng
Date: January 2, 2021
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


First,library the packages
```{r Library, message=FALSE}
library(tidyverse)
library(tmap)
library(geojsonio)
library(plotly)
library(rgdal)
library(broom)
library(mapview)
library(crosstalk)
library(sf)
library(sp)
library(spdep)
library(car)
library(fs)
library(janitor)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(forcats)
library(corrr)
```

## Read the CSV data

```{r}
maindata<-read.csv("data/Crime rate 2016/0005 assignment data.csv")

is.data.frame(maindata)
```

## use ggplot to malp plot
```{r}
ggplot(maindata,aes(x=year,y=GDP..billion.))+
  geom_line(color="#56b4e9",size = 1.2)+
  scale_y_continuous(name = "GDP(billion)",labels = scales::comma)+
  xlab(bquote("Time"))+
  scale_x_continuous(breaks = seq(1,2019,1),limits = c(2010, 2019))

ggplot(maindata,aes(x=year,y=population.k.))+
  geom_line(color="#56b4e9",size = 1.2)+
  scale_y_continuous(name = "population(thousand)",labels = scales::comma)+
  xlab(bquote("Time"))+
  scale_x_continuous(breaks = seq(1,2019,1),limits = c(2010, 2019))

ggplot(maindata,aes(x=year,y=house.price.mean..k.))+
  geom_line(color="#56b4e9",size = 1.2)+
  scale_y_continuous(name = "House price(thousand)",labels = scales::comma)+
  xlab(bquote("Time"))+
  scale_x_continuous(breaks = seq(1,2019,1),limits = c(2010, 2019))

ggplot(maindata,aes(x=year,y=employees.k.))+
  geom_line(color="#56b4e9",size = 1.2)+
  scale_y_continuous(name = "employees(thousand)",labels = scales::comma)+
  xlab(bquote("Time"))+
  scale_x_continuous(breaks = seq(1,2019,1),limits = c(2010, 2019))

ggplot(maindata,aes(x=year,y=Crime.number))+
  geom_line(color="#56b4e9",size = 1.2)+
  scale_y_continuous(name = "Crime.number",labels = scales::comma)+
  xlab(bquote("Time"))+
  scale_x_continuous(breaks = seq(1,2019,1),limits = c(2010, 2019))

```

## test variable 
```{r message=FALSE}
library(corrr)

Correlation <- maindata%>%
  dplyr::select(population.k.,
                GDP..billion.,
                house.price.mean..k.,
                employees.k.) %>%
  correlate() 

rplot(Correlation)
```

## test GDP&housing pricing
```{r message=FALSE}
Correlation2 <- maindata%>%
  dplyr::select(
                GDP..billion.,
               
                house.price.mean..k.,) %>%
  correlate() 

rplot(Correlation2)
```

## multiple regression model
```{r}
library(broom)
Regressiondata<- maindata%>%
  dplyr::select(Crime.number, 
                population.k.,
                GDP..billion.,
                house.price.mean..k.,
                employees.k.)

model1 <- Regressiondata %>%
  lm(Crime.number ~
       population.k.+ GDP..billion.+ house.price.mean..k.+ employees.k.,
     data=.)

summary(model1)

tidy(model1)
```

## Test vif
```{r}
vif(model1)
```

## multiple regression model2
```{r}
Regressiondata2<- maindata%>%
  dplyr::select(Crime.number, 
                population.k.,
                GDP..billion.,
                employees.k.)

model2 <- Regressiondata2 %>%
  lm(Crime.number ~
       population.k.+ GDP..billion.+ employees.k.,
     data=.)

summary(model2)

```

## test modle2 vif
```{r}
vif(model2)
```

## Standard Autocorrelation
```{r}
model_data <- model2 %>%
  augment(., Regressiondata2)


DW <- durbinWatsonTest(model2)
tidy(DW)
```

## spatial-autocorrelation-Moran’s I
```{r}
Chicagowards<-dir_info(here::here("data", 
                                 "Boundaries Wards"))%>%
  dplyr::filter(str_detect(path, 
                           "geo_export_6f1ca57a-6a70-4094-b008-70eace180952.shp"))%>%
  dplyr::select(path)%>%
  pull()%>%
  st_read()

ChicagowardProfiles<-read.csv("data/Crime rate 2016/population2.csv")

ChiwardProfiles <- Chicagowards%>%
  left_join(.,
            ChicagowardProfiles, 
            by = c("ward" = "Location"))


coordsW <- ChiwardProfiles%>%
  st_centroid()%>%
  st_geometry()

plot(coords)

LWard_nb <- ChiwardProfiles %>%
  poly2nb(., queen=T)

plot(LWard_nb, st_geometry(coordsW), col="red")

Lward.queens_weight <- LWard_nb %>%
  nb2listw(., style="C")
```

## spatial-autocorrelation-Moran’s I
```{r}
spatial <- ChicagowardProfiles %>%
  dplyr::select(total.change)%>%
  pull()%>%
  moran.test(., Lward.queens_weight)%>%
  tidy()
spatial
```

## chicago population change in 2010-2016
```{r}
library(maptools)
library(rgdal)
library(ggplot2)
library(sp)
library(plyr)
library(tidyverse)
library(sf)

Chicago_map <- readOGR(here::here("data", 
                                   "Boundaries Wards",
                                   "geo_export_6f1ca57a-6a70-4094-b008-70eace180952.shp"))

Chicago_map1 <- fortify(Chicago_map) 
x <- Chicago_map@data 
xs <- data.frame(x,id=seq(0:49)-1) 
Chicago_map_data <- join(Chicago_map1, xs, type = "full")

ward<-read.csv("data/Crime rate 2016/2016 population.csv")

Chicago_data <- join(Chicago_map_data, ward, type="full",by="ward")
Chicago_data$Value<- cut(Chicago_data$total.change,breaks=c(-4377,-2193,0,2970,10333),labels=c('-4,376~-2,193','-2,192~0','1~2,970','2,971~10,333'),order=TRUE)
rhg_cols1 <- c("#db2d24","#fabb85","#c3cfc5","#4377b3") 

midpos <- function(AD1){mean(range(AD1,na.rm=TRUE))} 
centres <- ddply(Chicago_data,.(ward),colwise(midpos,.(long,lat)))
centres1<-centres

centres1$lat[centres1$ward==41]<-centres1$lat[centres1$ward==41]-0.005
centres1$lat[centres1$ward==38]<-centres1$lat[centres1$ward==38]-0.005
centres1$long[centres1$ward==39]<-centres1$long[centres1$ward==39]+0.01
centres1$long[centres1$ward==35]<-centres1$long[centres1$ward==35]+0.01
centres1$long[centres1$ward==36]<-centres1$long[centres1$ward==36]-0.02
centres1$lat[centres1$ward==36]<-centres1$lat[centres1$ward==36]+0.01
centres1$long[centres1$ward==30]<-centres1$long[centres1$ward==30]-0.025
centres1$lat[centres1$ward==30]<-centres1$lat[centres1$ward==30]-0.005
centres1$long[centres1$ward==32]<-centres1$long[centres1$ward==32]+0.01
centres1$long[centres1$ward==29]<-centres1$long[centres1$ward==29]+0.01
centres1$long[centres1$ward==2]<-centres1$long[centres1$ward==2]-0.01
centres1$lat[centres1$ward==2]<-centres1$lat[centres1$ward==2]+0.005
centres1$lat[centres1$ward==27]<-centres1$lat[centres1$ward==27]-0.005
centres1$lat[centres1$ward==28]<-centres1$lat[centres1$ward==28]+0.01
centres1$long[centres1$ward==28]<-centres1$long[centres1$ward==28]-0.01
centres1$lat[centres1$ward==22]<-centres1$lat[centres1$ward==22]+0.01
centres1$lat[centres1$ward==12]<-centres1$lat[centres1$ward==12]-0.01
centres1$long[centres1$ward==14]<-centres1$long[centres1$ward==14]+0.01
centres1$lat[centres1$ward==13]<-centres1$lat[centres1$ward==13]+0.01
centres1$long[centres1$ward==13]<-centres1$long[centres1$ward==13]-0.02
centres1$lat[centres1$ward==20]<-centres1$lat[centres1$ward==20]-0.01
centres1$long[centres1$ward==16]<-centres1$long[centres1$ward==16]+0.02
centres1$long[centres1$ward==15]<-centres1$long[centres1$ward==15]-0.01
centres1$lat[centres1$ward==15]<-centres1$lat[centres1$ward==15]+0.02
centres1$long[centres1$ward==6]<-centres1$long[centres1$ward==6]+0.01
centres1$lat[centres1$ward==6]<-centres1$lat[centres1$ward==6]+0.01
centres1$long[centres1$ward==19]<-centres1$long[centres1$ward==19]+0.02
centres1$lat[centres1$ward==19]<-centres1$lat[centres1$ward==19]-0.01
centres1$lat[centres1$ward==10]<-centres1$lat[centres1$ward==10]-0.01
centres1$long[centres1$ward==5]<-centres1$long[centres1$ward==5]+0.005

ggplot() +
  geom_polygon(data=Chicago_data,aes(x=long,y=lat,group = group, fill = Value),colour="grey30",size=0.05) +
  geom_text(data=centres1,aes(x=long,y=lat,label=ward),size=2,col="black",fontface = "bold")+
  scale_fill_manual(values=rhg_cols1)+  
  guides(fill=guide_legend(title='Pop.Change 2010-16'))+
  coord_map("polyconic") +
  theme(                            
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )
```

## 2016 Theft distribute in Chicago
```{r}
Chicago_map <- readOGR(here::here("data", 
                                   "Boundaries Wards",
                                   "geo_export_6f1ca57a-6a70-4094-b008-70eace180952.shp"))

Chicago_map1 <- fortify(Chicago_map) 
x <- Chicago_map@data 
xs <- data.frame(x,id=seq(0:49)-1) 
Chicago_map_data <- join(Chicago_map1, xs, type = "full")

ward<-read.csv("data/Crime rate 2016/THEFT.csv")
ward_n<-data.frame(table(ward$Ward))
names(ward_n)<-c("ward","count")

Chicago_data <- join(Chicago_map_data, ward_n, type="full")
Chicago_data$Value<- cut(Chicago_data$count,breaks=c(0,1000,2000,3000,4000,5000,8000),labels=c('0~1000','1000~2000','2000~3000','3000~4000','4000-5000','5000+'),right=FALSE,order=TRUE)
rhg_cols1 <- c("#fcf7da","#f8e6ac","#efc18e","#af5f50","#8b2b1d","#441c19") 

midpos <- function(AD1){mean(range(AD1,na.rm=TRUE))} 
centres <- ddply(Chicago_data,.(ward),colwise(midpos,.(long,lat)))
centres1<-centres

centres1$lat[centres1$ward==41]<-centres1$lat[centres1$ward==41]-0.005
centres1$lat[centres1$ward==38]<-centres1$lat[centres1$ward==38]-0.005
centres1$long[centres1$ward==39]<-centres1$long[centres1$ward==39]+0.01
centres1$long[centres1$ward==35]<-centres1$long[centres1$ward==35]+0.01
centres1$long[centres1$ward==36]<-centres1$long[centres1$ward==36]-0.02
centres1$lat[centres1$ward==36]<-centres1$lat[centres1$ward==36]+0.01
centres1$long[centres1$ward==30]<-centres1$long[centres1$ward==30]-0.025
centres1$lat[centres1$ward==30]<-centres1$lat[centres1$ward==30]-0.005
centres1$long[centres1$ward==32]<-centres1$long[centres1$ward==32]+0.01
centres1$long[centres1$ward==29]<-centres1$long[centres1$ward==29]+0.01
centres1$long[centres1$ward==2]<-centres1$long[centres1$ward==2]-0.01
centres1$lat[centres1$ward==2]<-centres1$lat[centres1$ward==2]+0.005
centres1$lat[centres1$ward==27]<-centres1$lat[centres1$ward==27]-0.005
centres1$lat[centres1$ward==28]<-centres1$lat[centres1$ward==28]+0.01
centres1$long[centres1$ward==28]<-centres1$long[centres1$ward==28]-0.01
centres1$lat[centres1$ward==22]<-centres1$lat[centres1$ward==22]+0.01
centres1$lat[centres1$ward==12]<-centres1$lat[centres1$ward==12]-0.01
centres1$long[centres1$ward==14]<-centres1$long[centres1$ward==14]+0.01
centres1$lat[centres1$ward==13]<-centres1$lat[centres1$ward==13]+0.01
centres1$long[centres1$ward==13]<-centres1$long[centres1$ward==13]-0.02
centres1$lat[centres1$ward==20]<-centres1$lat[centres1$ward==20]-0.01
centres1$long[centres1$ward==16]<-centres1$long[centres1$ward==16]+0.02
centres1$long[centres1$ward==15]<-centres1$long[centres1$ward==15]-0.01
centres1$lat[centres1$ward==15]<-centres1$lat[centres1$ward==15]+0.02
centres1$long[centres1$ward==6]<-centres1$long[centres1$ward==6]+0.01
centres1$lat[centres1$ward==6]<-centres1$lat[centres1$ward==6]+0.01
centres1$long[centres1$ward==19]<-centres1$long[centres1$ward==19]+0.02
centres1$lat[centres1$ward==19]<-centres1$lat[centres1$ward==19]-0.01
centres1$lat[centres1$ward==10]<-centres1$lat[centres1$ward==10]-0.01
centres1$long[centres1$ward==5]<-centres1$long[centres1$ward==5]+0.005

ggplot(Chicago_data, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = Value),colour="grey30",size=0.05) +
  geom_text(data=centres1,aes(x=long,y=lat,label=ward),size=2,col="black",fontface = "bold")+
  scale_fill_manual(values=rhg_cols1)+  
  guides(fill=guide_legend(title='Crime number'))+
  coord_map("polyconic") +
  theme(                            
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )

```

## 2016 Battery distribute in Chicago
```{r}
Chicago_map <- readOGR(here::here("data", 
                                   "Boundaries Wards",
                                   "geo_export_6f1ca57a-6a70-4094-b008-70eace180952.shp"))

Chicago_map1 <- fortify(Chicago_map) 
x <- Chicago_map@data 
xs <- data.frame(x,id=seq(0:49)-1) 
Chicago_map_data <- join(Chicago_map1, xs, type = "full")

ward<-read.csv("data/Crime rate 2016/BATTERY.csv")
ward_n<-data.frame(table(ward$Ward))
names(ward_n)<-c("ward","count")

Chicago_data <- join(Chicago_map_data, ward_n, type="full")
Chicago_data$Value<- cut(Chicago_data$count,breaks=c(0,500,1000,1500,2000,2500,3000),labels=c('0~500','500~1000','1000~1500','1500~2000','2000~2500','2500~3000'),right=FALSE,order=TRUE)
rhg_cols1 <- c("#fcf7da","#f8e6ac","#efc18e","#af5f50","#8b2b1d","#441c19") 

midpos <- function(AD1){mean(range(AD1,na.rm=TRUE))} 
centres <- ddply(Chicago_data,.(ward),colwise(midpos,.(long,lat)))
centres1<-centres

centres1$lat[centres1$ward==41]<-centres1$lat[centres1$ward==41]-0.005
centres1$lat[centres1$ward==38]<-centres1$lat[centres1$ward==38]-0.005
centres1$long[centres1$ward==39]<-centres1$long[centres1$ward==39]+0.01
centres1$long[centres1$ward==35]<-centres1$long[centres1$ward==35]+0.01
centres1$long[centres1$ward==36]<-centres1$long[centres1$ward==36]-0.02
centres1$lat[centres1$ward==36]<-centres1$lat[centres1$ward==36]+0.01
centres1$long[centres1$ward==30]<-centres1$long[centres1$ward==30]-0.025
centres1$lat[centres1$ward==30]<-centres1$lat[centres1$ward==30]-0.005
centres1$long[centres1$ward==32]<-centres1$long[centres1$ward==32]+0.01
centres1$long[centres1$ward==29]<-centres1$long[centres1$ward==29]+0.01
centres1$long[centres1$ward==2]<-centres1$long[centres1$ward==2]-0.01
centres1$lat[centres1$ward==2]<-centres1$lat[centres1$ward==2]+0.005
centres1$lat[centres1$ward==27]<-centres1$lat[centres1$ward==27]-0.005
centres1$lat[centres1$ward==28]<-centres1$lat[centres1$ward==28]+0.01
centres1$long[centres1$ward==28]<-centres1$long[centres1$ward==28]-0.01
centres1$lat[centres1$ward==22]<-centres1$lat[centres1$ward==22]+0.01
centres1$lat[centres1$ward==12]<-centres1$lat[centres1$ward==12]-0.01
centres1$long[centres1$ward==14]<-centres1$long[centres1$ward==14]+0.01
centres1$lat[centres1$ward==13]<-centres1$lat[centres1$ward==13]+0.01
centres1$long[centres1$ward==13]<-centres1$long[centres1$ward==13]-0.02
centres1$lat[centres1$ward==20]<-centres1$lat[centres1$ward==20]-0.01
centres1$long[centres1$ward==16]<-centres1$long[centres1$ward==16]+0.02
centres1$long[centres1$ward==15]<-centres1$long[centres1$ward==15]-0.01
centres1$lat[centres1$ward==15]<-centres1$lat[centres1$ward==15]+0.02
centres1$long[centres1$ward==6]<-centres1$long[centres1$ward==6]+0.01
centres1$lat[centres1$ward==6]<-centres1$lat[centres1$ward==6]+0.01
centres1$long[centres1$ward==19]<-centres1$long[centres1$ward==19]+0.02
centres1$lat[centres1$ward==19]<-centres1$lat[centres1$ward==19]-0.01
centres1$lat[centres1$ward==10]<-centres1$lat[centres1$ward==10]-0.01
centres1$long[centres1$ward==5]<-centres1$long[centres1$ward==5]+0.005

ggplot(Chicago_data, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = Value),colour="grey30",size=0.05) +
  geom_text(data=centres1,aes(x=long,y=lat,label=ward),size=2,col="black",fontface = "bold")+
  scale_fill_manual(values=rhg_cols1)+  
  guides(fill=guide_legend(title='Crime number'))+
  coord_map("polyconic") +
  theme(                            
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )
```

## 2016 Assault distribute in Chicago
```{r}
Chicago_map <- readOGR(here::here("data", 
                                   "Boundaries Wards",
                                   "geo_export_6f1ca57a-6a70-4094-b008-70eace180952.shp"))

Chicago_map1 <- fortify(Chicago_map) 
x <- Chicago_map@data 
xs <- data.frame(x,id=seq(0:49)-1) 
Chicago_map_data <- join(Chicago_map1, xs, type = "full")

ward<-read.csv("data/Crime rate 2016/ASSAULT.csv")
ward_n<-data.frame(table(ward$Ward))
names(ward_n)<-c("ward","count")

Chicago_data <- join(Chicago_map_data, ward_n, type="full")
Chicago_data$Value<- cut(Chicago_data$count,breaks=c(0,500,1000,1500,2000,2500,3000),labels=c('0~500','500~1000','1000~1500','1500~2000','2000~2500','2500~3000'),right=FALSE,order=TRUE)
rhg_cols1 <- c("#fcf7da","#f8e6ac","#efc18e","#af5f50","#8b2b1d","#441c19") 

midpos <- function(AD1){mean(range(AD1,na.rm=TRUE))} 
centres <- ddply(Chicago_data,.(ward),colwise(midpos,.(long,lat)))
centres1<-centres

centres1$lat[centres1$ward==41]<-centres1$lat[centres1$ward==41]-0.005
centres1$lat[centres1$ward==38]<-centres1$lat[centres1$ward==38]-0.005
centres1$long[centres1$ward==39]<-centres1$long[centres1$ward==39]+0.01
centres1$long[centres1$ward==35]<-centres1$long[centres1$ward==35]+0.01
centres1$long[centres1$ward==36]<-centres1$long[centres1$ward==36]-0.02
centres1$lat[centres1$ward==36]<-centres1$lat[centres1$ward==36]+0.01
centres1$long[centres1$ward==30]<-centres1$long[centres1$ward==30]-0.025
centres1$lat[centres1$ward==30]<-centres1$lat[centres1$ward==30]-0.005
centres1$long[centres1$ward==32]<-centres1$long[centres1$ward==32]+0.01
centres1$long[centres1$ward==29]<-centres1$long[centres1$ward==29]+0.01
centres1$long[centres1$ward==2]<-centres1$long[centres1$ward==2]-0.01
centres1$lat[centres1$ward==2]<-centres1$lat[centres1$ward==2]+0.005
centres1$lat[centres1$ward==27]<-centres1$lat[centres1$ward==27]-0.005
centres1$lat[centres1$ward==28]<-centres1$lat[centres1$ward==28]+0.01
centres1$long[centres1$ward==28]<-centres1$long[centres1$ward==28]-0.01
centres1$lat[centres1$ward==22]<-centres1$lat[centres1$ward==22]+0.01
centres1$lat[centres1$ward==12]<-centres1$lat[centres1$ward==12]-0.01
centres1$long[centres1$ward==14]<-centres1$long[centres1$ward==14]+0.01
centres1$lat[centres1$ward==13]<-centres1$lat[centres1$ward==13]+0.01
centres1$long[centres1$ward==13]<-centres1$long[centres1$ward==13]-0.02
centres1$lat[centres1$ward==20]<-centres1$lat[centres1$ward==20]-0.01
centres1$long[centres1$ward==16]<-centres1$long[centres1$ward==16]+0.02
centres1$long[centres1$ward==15]<-centres1$long[centres1$ward==15]-0.01
centres1$lat[centres1$ward==15]<-centres1$lat[centres1$ward==15]+0.02
centres1$long[centres1$ward==6]<-centres1$long[centres1$ward==6]+0.01
centres1$lat[centres1$ward==6]<-centres1$lat[centres1$ward==6]+0.01
centres1$long[centres1$ward==19]<-centres1$long[centres1$ward==19]+0.02
centres1$lat[centres1$ward==19]<-centres1$lat[centres1$ward==19]-0.01
centres1$lat[centres1$ward==10]<-centres1$lat[centres1$ward==10]-0.01
centres1$long[centres1$ward==5]<-centres1$long[centres1$ward==5]+0.005

ggplot(Chicago_data, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = Value),colour="grey30",size=0.05) +
  geom_text(data=centres1,aes(x=long,y=lat,label=ward),size=2,col="black",fontface = "bold")+
  scale_fill_manual(values=rhg_cols1)+  
  guides(fill=guide_legend(title='Crime number'))+
  coord_map("polyconic") +
  theme(                            
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )

```

## 2016 Criminal Damage distribute in Chicago
```{r}
Chicago_map <- readOGR(here::here("data", 
                                   "Boundaries Wards",
                                   "geo_export_6f1ca57a-6a70-4094-b008-70eace180952.shp"))

Chicago_map1 <- fortify(Chicago_map) 
x <- Chicago_map@data 
xs <- data.frame(x,id=seq(0:49)-1) 
Chicago_map_data <- join(Chicago_map1, xs, type = "full")

ward<-read.csv("data/Crime rate 2016/CRIMINAL DAMAGE.csv")
ward_n<-data.frame(table(ward$Ward))
names(ward_n)<-c("ward","count")

Chicago_data <- join(Chicago_map_data, ward_n, type="full")
Chicago_data$Value<- cut(Chicago_data$count,breaks=c(0,500,1000,1500,2000,2500,3000),labels=c('0~500','500~1000','1000~1500','1500~2000','2000~2500','2500~3000'),right=FALSE,order=TRUE)
rhg_cols1 <- c("#fcf7da","#f8e6ac","#efc18e","#af5f50","#8b2b1d","#441c19") 

midpos <- function(AD1){mean(range(AD1,na.rm=TRUE))} 
centres <- ddply(Chicago_data,.(ward),colwise(midpos,.(long,lat)))
centres1<-centres

centres1$lat[centres1$ward==41]<-centres1$lat[centres1$ward==41]-0.005
centres1$lat[centres1$ward==38]<-centres1$lat[centres1$ward==38]-0.005
centres1$long[centres1$ward==39]<-centres1$long[centres1$ward==39]+0.01
centres1$long[centres1$ward==35]<-centres1$long[centres1$ward==35]+0.01
centres1$long[centres1$ward==36]<-centres1$long[centres1$ward==36]-0.02
centres1$lat[centres1$ward==36]<-centres1$lat[centres1$ward==36]+0.01
centres1$long[centres1$ward==30]<-centres1$long[centres1$ward==30]-0.025
centres1$lat[centres1$ward==30]<-centres1$lat[centres1$ward==30]-0.005
centres1$long[centres1$ward==32]<-centres1$long[centres1$ward==32]+0.01
centres1$long[centres1$ward==29]<-centres1$long[centres1$ward==29]+0.01
centres1$long[centres1$ward==2]<-centres1$long[centres1$ward==2]-0.01
centres1$lat[centres1$ward==2]<-centres1$lat[centres1$ward==2]+0.005
centres1$lat[centres1$ward==27]<-centres1$lat[centres1$ward==27]-0.005
centres1$lat[centres1$ward==28]<-centres1$lat[centres1$ward==28]+0.01
centres1$long[centres1$ward==28]<-centres1$long[centres1$ward==28]-0.01
centres1$lat[centres1$ward==22]<-centres1$lat[centres1$ward==22]+0.01
centres1$lat[centres1$ward==12]<-centres1$lat[centres1$ward==12]-0.01
centres1$long[centres1$ward==14]<-centres1$long[centres1$ward==14]+0.01
centres1$lat[centres1$ward==13]<-centres1$lat[centres1$ward==13]+0.01
centres1$long[centres1$ward==13]<-centres1$long[centres1$ward==13]-0.02
centres1$lat[centres1$ward==20]<-centres1$lat[centres1$ward==20]-0.01
centres1$long[centres1$ward==16]<-centres1$long[centres1$ward==16]+0.02
centres1$long[centres1$ward==15]<-centres1$long[centres1$ward==15]-0.01
centres1$lat[centres1$ward==15]<-centres1$lat[centres1$ward==15]+0.02
centres1$long[centres1$ward==6]<-centres1$long[centres1$ward==6]+0.01
centres1$lat[centres1$ward==6]<-centres1$lat[centres1$ward==6]+0.01
centres1$long[centres1$ward==19]<-centres1$long[centres1$ward==19]+0.02
centres1$lat[centres1$ward==19]<-centres1$lat[centres1$ward==19]-0.01
centres1$lat[centres1$ward==10]<-centres1$lat[centres1$ward==10]-0.01
centres1$long[centres1$ward==5]<-centres1$long[centres1$ward==5]+0.005

ggplot(Chicago_data, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = Value),colour="grey30",size=0.05) +
  geom_text(data=centres1,aes(x=long,y=lat,label=ward),size=2,col="black",fontface = "bold")+
  scale_fill_manual(values=rhg_cols1)+  
  guides(fill=guide_legend(title='Crime number'))+
  coord_map("polyconic") +
  theme(                            
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )
```


